Near and Mid-infrared properties of known redshift $z\geq5$ Quasars

### 2019-06-14 tex/VHzQ.tex
moved average_NEOWISE_lightcurves.py
tex/VHzQ.pdf final Friday evening push...

Recently, \citet{Assef2018} released two large catalogues of AGN
candidates identified across 30,000 deg$^2$ of extragalactic sky from
the WISE AllWISE Data Release. The ``R90'' catalogue, contains 4.5M
AGN candidates at 90\% reliability (and $\approx$150 AGN candidates
per deg$^2$) while the ``C75'' catalogue consists of 20.9M AGN
candidates at 75\% completeness (and ($\approx$700 AGN candidates per
deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
catalogues, produces 42 matches with the R90 sample and 98 matches
with the C75 sample. Both catalogues unsurprisingly match to the
ultraluminous quasar SDSS J0100+2802 \citep{Wu2015} while the C75, but
not the R90 catalogue matches to the first redshift $z>7$ quasar ULAS
J1120+0641 \citep{Mortlock2011}. Neither catalogue matches to the
current highest-redshift object J1342+0928 \citep{Banados2018}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{SurfaceDensity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}\label{sec:conclusions}
In this study, we have, for the first time, compiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assembled the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that:

\begin{itemize}
    \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;  
    \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though 
      efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
    \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
    \item The 14 objects that are not detected in the NIR are due to lack of coverage rather than lack of depth; 
   \item 362 ( 78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
 \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
 \item 32 of the quasars had enough NIR measurements and sufficient NIR measurements and signal-to-noise to look for variability. Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529. 2 other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability. 
\end{itemize}

>>>>

\citet{Secrest2015} present an all-sky sample of $\approx$1.35 million active galactic nuclei (AGNs) 
meeting a two-color, (W1-W2) vs. (W2-W3) infrared photometric selection criteria for AGNs as applied to sources from the Wide-field Infrared Survey Explorer final catalog release (AllWISE). 
%%
Recently, \citet{Assef2018} released two large catalogues of AGN
candidates identified across 30,000 deg$^2$ of extragalactic sky from
the WISE AllWISE Data Release. The ``R90'' catalogue, contains 4.5M
AGN candidates at 90\% reliability (and $\approx$150 AGN candidates
per deg$^2$) while the ``C75'' catalogue consists of 20.9M AGN
candidates at 75\% completeness (and ($\approx$700 AGN candidates per
deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
catalogues, produces 42 matches with the R90 sample and 98 matches
with the C75 sample. Both catalogues unsurprisingly match to the
ultraluminous quasar SDSS J0100+2802 \citep{Wu2015} while the C75, but
not the R90 catalogue matches to the first redshift $z>7$ quasar ULAS
J1120+0641 \citep{Mortlock2011}. Neither catalogue matches to the
current highest-redshift object J1342+0928 \citep{Banados2018}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{SurfaceDensity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}\label{sec:conclusions}
In this study, we have, for the first time, compiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assembled the NIR
($Z, Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects and given their detection rates. We find that:

\begin{itemize}
    \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;  
    \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though 
      efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
    \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
    \item The 14 objects that are not detected in the NIR are due to lack of coverage rather than lack of depth; 
   \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
 \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
 \item 32 of the quasars had enough NIR measurements and sufficient NIR measurements and signal-to-noise to look for variability. Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529. 2 other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability. 
\end{itemize}
